Parameter Space Representation of Pareto Front to Explore Hardware-Software Dependencies

### 2014-07-27 paper.tex
AA: aggiustato fino a initialization phase

\newcommand{\comment}[1]{\textcolor{red}{AA: \bf #1}}
%\newcommand\comment[1]{} % When you enable this lines, all the notes will disappear

@@

%\maketitle
\begin{abstract}
Embedded Systems Design often requires conflicting objectives to be
optimized with an appropriate choice of hardware/software parameters .
Interdependencies among these parameters can make this task even more
difficult, since an a-priori knowledge of them would  be required to
develop an analytical model of the system. In this work we present PS,
a multiobjective exploration algorithm that introduces the notion of
Parameters Space Representation. After a detailed formal description
of the algorithm and its concepts, we show a hardware/software
exploration case study. Qualitative and quantitative comparisons of PS
against a well-know multiobjective genetic approach demonstrate that,
while not outperforming it in terms of dominance, the proposed
approach can trade the uniformity and granularity qualities of the
solutions found for obtaining larger Pareto sets, thus representing a
further choice for designer when objective constrains allow it.
\end{abstract}

@@

>>>>

\newcommand{\comment}[1]{\textcolor{red}{\bf #1}}
%\newcommand\comment[1]{} % When you enable this lines, all the notes will disappear

@@

%\maketitle
\begin{abstract}
Embedded Systems Design requires conflicting objectives to be
optimized with an appropriate choice of hardware/software parameters. A simulation campaign guides the design in finding the best trade-offs, but, due to the big number of possible configurations, it is unfeasible to simulate all of them. For these reason Design Space Exploration (DSE) algorithms aim at finding near-optimal system configurations, only simulating a subset of them.

In this work we present PS, a new multiobjective exploration algorithm. The basic idea is to recognize \emph{interesting}, i.e. regions of the configuration space that are proving to provide better configurations w.r.t. other ones. PS evaluates more configurations in interesting regions while exploring less thoroughly the rest of the configuration space. After a detailed formal description
of the algorithm and the underlying concepts, we show a hardware/software
exploration case study. Qualitative and quantitative comparisons of PS
against a well-know multiobjective genetic approach demonstrate that,
while not outperforming it in terms of dominance, the proposed
approach can trade the uniformity and granularity qualities of the
solutions found for obtaining larger Pareto sets, thus representing a
further choice for designer when objective constrains allow it.
\end{abstract}

@@

\comment{AA: Esportare di
nuovo tutte le immagini libreoffice - svg - eps che viene meglio, come
si vede in \figR{3}. Aggiustare i nomi degli assi che in alcune figure
sono sbagliati. O forse basta esportarli col nuovo libreoffice che fa
meglio DP: hai ragione, ma forse siamo fuori tempo limite per queste
cose}
